Exploratory and descriptive analysis

### 2023-04-08 notebook/exploratory.qmd
Add more descriptive graphs

---
title: EDA
---

@@

# Timeline of registration

TODO

@@

```{r province-count-distribution, warning=FALSE}
ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, color = "white", size = 0.1, boundary = 0) +
  labs(x = "Number of provinces", y = "Count",
       title = "Distribution of province counts") +
  theme_ongo()
```

@@

```{r ongo-map, fig.height=5, fig.width=7, message=FALSE, warning=FALSE}
# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
labeldata <- mapdata |> 
  filter(ro_count > 0)

plot_map <- ggplot() +
  geom_sf(data = mapdata,
          aes(fill = ro_count), color = "white") +
  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1,
                       guide = "none") +
  geom_label_repel(data = labeldata, 
                   aes(label = ro_count, geometry = geometry),
                   stat = "sf_coordinates",
                   size = 3) +
  theme_void()
plot_map
```

>>>>

---
title: Exploratory and descriptive analysis
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "80%", collapse = TRUE,
                      dev = "png", dev.args = list(type = "cairo-png"))

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

@@

# Timeline of ONGO registrations

```{r plot-registration-timeline}
ggplot(ongo, aes(x = registration_date)) +
  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
                 fill = clrs[6], color = "white") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  labs(x = NULL, y = "Count of new ONGO registrations") +
  theme_ongo()
```

@@

```{r province-count-distribution, warning=FALSE}
ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  labs(x = "Number of provinces ONGOs are registered in", y = "Count") +
  theme_ongo()
```

# Issue areas

```{r plot-ongo-issues}
issue_count <- ongo |> 
  drop_na(work_field_code1) |> 
  group_by(work_field_code1) |>
  summarize(n = n()) |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, n))

ggplot(issue_count, aes(y = work_field_code1, x = n)) +
  geom_col(fill = clrs[5]) +
  labs(x = "Count of ONGOs", y = NULL) +
  theme_ongo()
```

@@

```{r ongo-map, fig.height=5, fig.width=7, message=FALSE, warning=FALSE}
# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
ggplot() +
  geom_sf(data = mapdata, aes(fill = ro_count), 
          linewidth = 0.3, color = "white") +
  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none") +
  geom_label_repel(data = filter(mapdata, ro_count > 0), 
                   aes(label = ro_count, geometry = geometry),
                   stat = "sf_coordinates", seed = 1234, label.size = 0.1, size = 3,
                   segment.color = "black", segment.size = 0.5, min.segment.length = 0) +
  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
  theme_void()
```
